---
title: "Path Analysis AI Demo"
output: 
  html_document:
    theme: flatly
    toc: true
    toc_float: true
    css: styles.css
params:
  pid: "[ADD PROPERTY ID HERE]"
  mid: "[ADD MEASUREMENT ID HERE]"
  base_cats: 
  google_account: "[ADD GOOGLE ACCOUNT HERE]"
---

Primary Goal: Build an AI LLM model solution which can ingest pre-processed data (structured data schema) and a path analysis query user prompt, and return a tokenized text response or report

Obj 1: Demo proof of concept with Example Case
- Example Query: Can we ID and rank the page paths users take on their site journey which result in a conversion within a single session? And what proportion each converting paths makes of total? 

Obj 2: Build AI model pipeline that can receive this expected data structure

Obj 3: Solution data processing to work on multiple data sources (Any site path data)


```{r setup, include = FALSE, warning = FALSE, message = FALSE}
# Check for packages needed and then load the packages
if (!require("pacman")) install.packages("pacman")
pacman::p_load(tidyverse,
               googleAnalyticsR,
               googlesheets4,
               scales,
               htmltools,  # Adding logo
               knitr,
               kableExtra,
               sditools)

# Set your GA4 property variables
pid <- params$pid 
mid <- params$mid
```


```{r Authenticate}
# Authenticate Google account
googleAnalyticsR::ga_auth(email = params$google_account)
```


```{r get_data}

# Get lists of all variables
df_variables <- ga_meta(propertyId = pid, version = 'data')

# Configure data pull: Use list to update below to select applicable variables and filters
pull_metrics <- c("customEvent:count_form_submission_successes")
pull_dimensions <- c("dateHourMinute","customUser:SESSIONID","customUser:GACLIENTID", "sessionSource", "sessionMedium", "pagePath", "landingPage", "customEvent:type")
pull_filters <- ga_data_filter(!("customUser:GACLIENTID" == "(not set)"))
date_range <- c("2023-11-1", "2024-1-29")

# Get data: Use variable list to select data for path analysis where conversion = form submission
df_event <- ga_data(
  pid,
  metrics = pull_metrics,
  dimensions = pull_dimensions,
  dim_filters = pull_filters,
  date_range = date_range,
  limit = 1000
)

```

```{r process data: create session_id and sort}
# Create a data frame with the inputs
data <- df_event %>%
  mutate(session_id = paste(`customUser:GACLIENTID`,`customUser:SESSIONID`, sep ="."))

sort_data <- data %>% 
  arrange(session_id, dateHourMinute)

```


```{r process data: sequence path}
# Initialize a new column to store the sequence of page paths, current session id, and current sequence
seq_data <- sort_data
seq_data$sequence <- NULL
current_session_id <- 0
current_sequence <- NULL

# Iterate through each session_id and fill in the sequence based on the page paths

for (i in 1:nrow(seq_data)) {
  if (seq_data$session_id[i] != current_session_id) {
    current_session_id <- seq_data$session_id[i]
    current_sequence <- seq_data$pagePath[i]
  } else {
    current_sequence <- paste(current_sequence, seq_data$pagePath[i], sep = " > ")
  }
  seq_data$sequence[i] <- current_sequence
}

# View the updated data frame with the sequence column
print(seq_data)
```

```{r process data: tag conversions}
# For Objective 1 Example Query: id sessions that result in conversion
converters <- data %>%
  filter(`customEvent:count_form_submission_successes` > 0, `customEvent:type` == "Gated Resource Form") %>%
  distinct(`session_id`) %>%
  pull()

tag_data <- seq_data %>% 
  filter(session_id %in% converters)


 converters <- data %>%
  filter(`customEvent:count_form_submission_successes` > 0) %>%
  distinct(`session_id`) %>%
  pull()
```


```{r compute path query measures and report}
# Filter only the sessions where conversion = TRUE
converted_sessions <- tag_data

# Filter only the complete path
converted_full_paths <- converted_sessions %>%
  group_by(session_id) %>%
  filter(sequence == max(sequence))
  
# Count the frequency of each sequence of page paths
sequence_counts <- table(converted_full_paths$sequence)

# Sort the sequences by count in descending order
sorted_sequences <- sort(sequence_counts, decreasing = TRUE)

# Report: Rank and proportion score of converting paths
rank_df <- data.frame(sorted_sequences)
path_report <- rank_df %>%
  mutate(rank = row_number(rank_df)) %>%
  mutate(conversionPath = Var1) %>%
  mutate(freq = Freq) %>% 
  mutate(prop = prop.table(sorted_sequences)) %>% 
  mutate(score = round(prop * 100)) %>% 
  select(rank, conversionPath, freq, prop, score)
```
